### 2025-07-08 acronyms/acronyms.tex
iso
risk indices
risk index
wsi
nsf
sfs

@@

@@

\newacronym{set}{SETS}{Socio-Environmental Technological System}

@@

@@

>>>>

\newacronym{iso}{ISO}{International Organization for Standardization}

@@

\newacronym{dcl}{DCL}{Dear Colleague Letter}

@@

\newacronym{set}{SETS}{Socio-Environmental Technological Systems}
\newacronym{sfs}{SFS}{Sustainable Future Scenarios}

@@

%%%%% water
\newacronym{adi}{ADI}{Agricultural Drought Index}
\newacronym{app}{AP}{Average Annual Rainfall Volume}
\newacronym{cq}{CI}{Consequence Subindex}
\newacronym{exi}{ExI}{Exposure Indicator}
\newacronym{hi}{HI}{Drought Hazard Subindex}
\newacronym{hdi}{HDI}{Hydrological Drought Index}
\newacronym{kde}{KDE}{Kernel Density Estimation}
\newacronym{mdi}{MDI}{Meteorological Drought Index}
\newacronym{ndi}{NDI}{Normalized Deficit Index}
\newacronym{ndc}{NDC}{Normalized Deficit Cumulated}
\newacronym{sic}{SIC}{Stress Index Cumulated}
\newacronym{sii}{SII}{Stress Index Intra-annual}
\newacronym{vi}{VI}{Vulnerability Indicator}
\newacronym{wri}{WSRI}{Water Shortage Risk Index}
\newacronym{wsi}{W-ScaRI}{Water Scarcity Risk Index}

@@

%\newacronym{}{}{}
